Interpolation of Sparse High-Dimensional Data\thanks {This work was supported by the National Science Foundation Grant CNS-1565314.}

### 2019-10-04 Paper_[2019-02]_NUMA/paper.tex
Nearly done with NUMA revisions. Ran new test for SVR and BoxSplines, integrated with old data.

The error bound provided is tight and that is easily observed by
considering the test function $q(x) = \|x\|_2^2,$ $x \in \mathbb{R}^d$
for $d \in \mathcal{N},$ using the simplex $X = \{\mathbf{0}, I\},$
where $I$ is the $d \times d$ identity matrix, and an approximation is
made at $z = \mathbf{1/2}.$ Now this setup yields

\vspace{-4mm}
$$ \gamma = 1, \qquad \sigma_d = 1, \qquad k = 1, \qquad x_0 =
\mathbf{0}, \qquad \hat q(x) = \langle\mathbf{1}, x - \mathbf{0}\rangle +
q(\mathbf{0}). $$
\vspace{-2mm}
\noindent Plugging these values into the Theorem, we get
\vspace{-2mm}

\begin{align*}
  \big|q(z) - \hat q(z)\big| \quad
  =& \quad \big|\|z\|_2^2 - \langle\mathbf{1},z\rangle\big| \\
  =& \quad \bigg| \frac{d}{4} - \frac{d}{2} \bigg| \quad = \quad \frac{d}{4} \\
  \leq& \quad \frac{\gamma \|z - x_0\|_2^2}{2} + \sqrt{d} \frac{\gamma k^2}
      {2 \sigma_d} \|z - x_0\|_2 \\
  =& \quad \frac{\|z\|_2^2 + \sqrt{d} \|z\|_2}{2} \\
  =& \quad \bigg(\frac{d}{4} + \frac{d}{4}\bigg)\ /\ 2 \quad = \quad \frac{d}{4}.
\end{align*}

In light of this error bound and analytic test, an empirical
evaluation of presented algorithms follows.

@@

The theoretical results constructed in Section \ref{sec:theory} for
(piecewise) linear interpolation are promising and apply directly to
Delaunay interpolation, however they are difficult to interpret in
context with approximation algorithms that do not have similar known
uniform error bounds. For that reason, this paper utilizes five
different data sets of varying dimension and application to construct
approximations and compare the accuracy of different techniques.

@@

\begin{table}
  \renewcommand{\arraystretch}{1.3}
  \centering
  \begin{tabular}{c|c|c|c|c}
     & $p = .05$ & $p = .01$ & $p = .001$ & $p = 10^{-6}$\\
    \hline
    Delaunay & $\mathbf{50.3}\%$ & $\mathit{43.5}\%$ & $\mathit{36.2}\%$ & $\mathit{24.7}\%$\\
    ShepMod & $\mathit{51.4}\%$ & $44.8\%$ & $38.1\%$ & $27.7\%$\\
    Voronoi & $52.6\%$ & $\mathbf{43.4}\%$ & $\mathbf{34.4}\%$ & $\mathbf{19.1}\%$\\
    BoxSpline & $99.5\%$ & $98.5\%$ & $96.6\%$ & $89.5\%$\\
  \end{tabular}
  \caption{Numerical counterpart of the histogram data presented in
    Figure \ref{fig:throughput-prediction}. The columns display the
    percent of null hypothesis rejections by the KS-test when provided
    different selections of $p$-values for each algorithm. The
    algorithm with the lowest rejection rate at each $p$ is boldface,
    while the second lowest is italicized.}
  \label{table:null-hypothesis-results}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l}
    Algorithm & \multicolumn{2}{c|}{Avg. \% Best} & \multicolumn{2}{c|}{\multilinecell{Avg. Fit or \\ Prep. Time (s)}} & \multicolumn{2}{c}{Avg. App. Time (s)}\\
    \hline
    MARS & \quad\quad$4$&$6$ & \,\quad$20$&$0$ & \quad\quad$0$&$001$\\
    SVR & $\mathit{21}$&$\mathit{1}$ & $\mathbf{0}$&$\mathbf{5}$ & $\mathbf{0}$&$\mathbf{0001}$\\
    MLP & $\mathbf{42}$&$\mathbf{1}$ & $200$&$0$ & $0$&$001$\\
    Delaunay & $6$&$0$ & $1$&$0$ & $1$&$0$\\
    ShepMod & $18$&$4$ & $\mathit{0}$&$\mathit{7}$ & $\mathbf{0}$&$\mathbf{0001}$\\
    LSHEP & $8$&$4$ & $2$&$0$ & $\mathbf{0}$&$\mathbf{0001}$\\
    Voronoi & $0$&$5$ & $1$&$0$ & $0$&$04$\\
    BoxSpline & $0$&$2$ & $0$&$8$ & $\mathit{0}$&$\mathit{0005}$\\
  \end{tabular}
  \caption{This average of Appendix Tables
    \ref{table:best-forest-fire}, \ref{table:best-parkinsons},
    \ref{table:best-weather}, and \ref{table:best-credit-card}
    provides a gross summary of overall results. The columns display
    (weighted equally by data set, \textit{not} points) the average
    frequency with which any algorithm provided the lowest absolute
    error approximation, the average time to fit/prepare, and the
    average time required to approximate one point. The times have
    been rounded to one significant digit, as reasonably large
    fluctuations may be observed due to implementation hardware.
    Interpolants provide the lowest error approximation for nearly one
    third of all data, while regressors occupy the other two
    thirds. This result is obtained without any customized tuning or
    preprocessing to maximize the performance of any given
    algorithm. In practice, tuning and preprocessing may have large
    effects on approximation performance.}
  \label{table:avg-performance}
\end{table}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l|r@{.}l|r@{.}l}
    \hline
    Algorithm & \multicolumn{2}{c|}{Min} & \multicolumn{2}{c|}{$25^{th}$} & \multicolumn{2}{c|}{$50^{th}$} & \multicolumn{2}{c|}{$75^{th}$} & \multicolumn{2}{c}{Max}\\
    \hline
    MARS & $0$&$00984$ & $3$&$11$ & $7$&$01$ & $\mathit{11}$&$\mathit{7}$ & $1090$&$0$\\
    SVR & $\mathit{0}$&$\mathit{00402}$ & $\mathbf{0}$&$\mathbf{243}$ & $\mathbf{0}$&$\mathbf{416}$ & $\mathbf{6}$&$\mathbf{19}$ & $1090$&$0$\\
    MLP & $0$&$0426$ & $2$&$63$ & $\mathit{5}$&$\mathit{27}$ & $14$&$0$ & $1090$&$0$\\
    Delaunay & $\mathbf{0}$&$\mathbf{00}$ & $1$&$98$ & $5$&$37$ & $13$&$1$ & $\mathit{1080}$&$\mathit{0}$\\
    ShepMod & $\mathbf{0}$&$\mathbf{00}$ & $\mathit{1}$&$\mathit{93}$ & $6$&$27$ & $16$&$0$ & $1090$&$0$\\
    LSHEP & $0$&$0400$ & $2$&$17$ & $8$&$87$ & $19$&$1$ & $\mathbf{1070}$&$\mathbf{0}$\\
    Voronoi & $0$&$00982$ & $3$&$65$ & $7$&$56$ & $15$&$6$ & $1090$&$0$\\
    BoxSpline & $\mathbf{0}$&$\mathbf{00}$ & $2$&$27$ & $5$&$91$ & $16$&$4$ & $1090$&$0$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    Figure \ref{fig:error-forest-fire}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    third quartile, and maximum absolute errors respectively. The
    minimum of each column is boldface, while the second lowest value
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-forest-fire}
\end{table}

\begin{table}[H]
  \centering
  \begin{tabular}{|c|r@{.}l| c |r@{.}l|r@{.}l|r@{.}l|}
    \cline{1-3}\cline{5-10}
    Algorithm & \multicolumn{2}{c|}{\% Best} &  & \multicolumn{2}{c|}{Fit/Prep. Time (s)} & \multicolumn{2}{c|}{App. Time (s)} & \multicolumn{2}{c|}{Total App. Time (s)}\\
    \cline{1-3}\cline{5-10}
    MARS & \quad$\mathit{7}$&$\mathit{7}$ &  & \quad\quad$29$&$1$ & \quad$0$&$00137$ & \quad\quad\quad$0$&$0686$\\
    SVR & $\mathbf{80}$&$\mathbf{2}$ &  & $\mathbf{0}$&$\mathbf{00584}$ & $\mathit{0}$&$\mathit{0000620}$ & $\mathit{0}$&$\mathit{00310}$\\
    MLP & $0$&$0$ &  & $32$&$8$ & $0$&$000871$ & $0$&$0436$\\
    Delaunay & $3$&$5$ &  & $0$&$0151$ & $0$&$0234$ & $1$&$18$\\
    ShepMod & $3$&$7$ &  & $\mathit{0}$&$\mathit{00634}$ & $0$&$0000644$ & $0$&$00322$\\
    LSHEP & $5$&$1$ &  & $0$&$0275$ & $\mathbf{0}$&$\mathbf{0000463}$ & $\mathbf{0}$&$\mathbf{00231}$\\
    Voronoi & $0$&$0$ &  & $0$&$0152$ & $0$&$000396$ & $0$&$0198$\\
    BoxSpline & $0$&$4$ &  & $0$&$00724$ & $0$&$0000978$ & $0$&$00489$\\
    \cline{1-3}\cline{5-10}
  \end{tabular}
  \caption{The left above shows how often each algorithm had the
    lowest absolute error approximating forest fire data in Table
    \ref{table:error-forest-fire}. On the right columns are median fit
    time of 454 points, median time for one approximation, and median
    time approximating 50 points.}
  \label{table:best-forest-fire}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l|r@{.}l|r@{.}l}
    \hline
    Algorithm & \multicolumn{2}{c|}{Min} & \multicolumn{2}{c|}{$25^{th}$} & \multicolumn{2}{c|}{$50^{th}$} & \multicolumn{2}{c|}{$75^{th}$} & \multicolumn{2}{c}{Max}\\
    \hline
    MARS & $0$&$00948$ & $9$&$98$ & $20$&$4$ & $32$&$9$ & $863$&$0$\\
    SVR & $0$&$00138$ & $3$&$17$ & $7$&$31$ & $12$&$6$ & $\mathbf{27}$&$\mathbf{5}$\\
    MLP & $0$&$0000239$ & $\mathit{0}$&$\mathit{533}$ & $\mathit{1}$&$\mathit{25}$ & $\mathbf{2}$&$\mathbf{84}$ & $39$&$3$\\
    Delaunay & $\mathit{3}$&$\mathit{72 \times 10^{-12}}$ & $1$&$20$ & $3$&$50$ & $7$&$67$ & $30$&$7$\\
    ShepMod & $\mathbf{0}$&$\mathbf{0}$ & $\mathbf{0}$&$\mathbf{255}$ & $\mathbf{0}$&$\mathbf{908}$ & $\mathit{3}$&$\mathit{43}$ & $34$&$5$\\
    LSHEP & $0$&$00254$ & $2$&$93$ & $7$&$16$ & $13$&$1$ & $\mathit{29}$&$\mathit{0}$\\
    Voronoi & $\mathbf{0}$&$\mathbf{0}$ & $1$&$29$ & $3$&$52$ & $6$&$87$ & $30$&$1$\\
    BoxSpline & $0$&$00287$ & $4$&$39$ & $9$&$10$ & $14$&$8$ & $41$&$3$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    Figure \ref{fig:error-parkinsons}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    third quartile, and maximum absolute errors respectively. The
    minimum of each column is boldface, while the second lowest value
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-parkinsons}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l|r@{.}l|r@{.}l}
    \hline
    Algorithm & \multicolumn{2}{c|}{Min} & \multicolumn{2}{c|}{$25^{th}$} & \multicolumn{2}{c|}{$50^{th}$} & \multicolumn{2}{c|}{$75^{th}$} & \multicolumn{2}{c}{Max}\\
    \hline
    MARS & $\mathit{6}$&$\mathit{45 \times 10^{-15}}$ & $\mathbf{2}$&$\mathbf{70 \times 10^{-14}}$ & $1$&$66$ & $1$&$96$ & $\mathit{53}$&$\mathit{3}$\\
    SVR & $0$&$0420$ & $0$&$143$ & $0$&$148$ & $\mathit{0}$&$\mathit{860}$ & $119$&$0$\\
    MLP & $0$&$0000689$ & $0$&$0337$ & $\mathbf{0}$&$\mathbf{0795}$ & $\mathbf{0}$&$\mathbf{264}$ & $\mathbf{5}$&$\mathbf{31}$\\
    Delaunay & $\mathbf{0}$&$\mathbf{0}$ & $0$&$187$ & $0$&$919$ & $2$&$72$ & $56$&$3$\\
    ShepMod & $\mathbf{0}$&$\mathbf{0}$ & $0$&$0957$ & $0$&$685$ & $2$&$90$ & $73$&$2$\\
    LSHEP & $\mathbf{0}$&$\mathbf{0}$ & $\mathit{0}$&$\mathit{0153}$ & $\mathit{0}$&$\mathit{106}$ & $1$&$17$ & $113$&$0$\\
    Voronoi & $\mathbf{0}$&$\mathbf{0}$ & $0$&$430$ & $1$&$28$ & $2$&$94$ & $83$&$8$\\
    BoxSpline & $\mathbf{0}$&$\mathbf{0}$ & $0$&$789$ & $2$&$06$ & $5$&$25$ & $119$&$0$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    Figure \ref{fig:error-weather}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    third quartile, and maximum absolute errors respectively. The
    minimum value of each column is boldface, while the second lowest
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-weather}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|c|r@{.}l| c |r@{.}l|r@{.}l|r@{.}l|}
    \cline{1-3}\cline{5-10}
    Algorithm & \multicolumn{2}{c|}{\% Best} &  & \multicolumn{2}{c|}{Fit/Prep. Time (s)} & \multicolumn{2}{c|}{App. Time (s)} & \multicolumn{2}{c|}{Total App. Time (s)}\\
    \cline{1-3}\cline{5-10}
    MARS & \,\,\,\,$10$&$7$ &  & \quad\quad\quad$\mathit{0}$&$\mathit{151}$ & \quad$0$&$000117$ & \quad\quad\quad\,\,$0$&$0304$\\
    SVR & $4$&$1$ &  & $\mathbf{0}$&$\mathbf{133}$ & $\mathbf{0}$&$\mathbf{0000947}$ & $\mathbf{0}$&$\mathbf{0246}$\\
    MLP & $\mathbf{56}$&$\mathbf{8}$ &  & $169$&$0$ & $0$&$00137$ & $0$&$356$\\
    Delaunay & $0$&$1$ &  & $0$&$664$ & $0$&$886$ & $230$&$0$\\
    ShepMod & $3$&$5$ &  & $0$&$265$ & $0$&$000128$ & $0$&$0333$\\
    LSHEP & $\mathit{28}$&$\mathit{4}$ &  & $0$&$874$ & $\mathit{0}$&$\mathit{0000975}$ & $\mathit{0}$&$\mathit{0254}$\\
    Voronoi & $0$&$2$ &  & $0$&$675$ & $0$&$0270$ & $7$&$01$\\
    BoxSpline & $0$&$3$ &  & $0$&$330$ & $0$&$000406$ & $0$&$106$\\
    \cline{1-3}\cline{5-10}
  \end{tabular}
  \caption{Left table shows how often each algorithm had the lowest
    absolute error approximating Sydney rainfall data in Table
    \ref{table:error-weather}. On the right columns are median fit
    time of 2349 points, median time for one approximation, and median
    time approximating 260 points.}
  \label{table:best-weather}
\end{table}

>>>>

The theoretical error bound is tight and that can be observed with the
test function $q(x) = \|x\|_2^2,$ $x \in \mathbb{R}^d$ for $d \in
\mathcal{N},$ and the simplex defined by vertices $X = \{\mathbf{0}, e_1,
\ldots, e_d\}$ where $e_i$ is $i$-th unit vector in $\mathbb{R}^d.$
The relevant constants to the error bound are

\vspace{-2mm}
$$ \gamma = 2, \qquad \sigma_d = 1, \qquad k = 1, \qquad x_0 =
\mathbf{0}, \qquad \hat q(x) = \langle\mathbf{1}, x - \mathbf{0}\rangle +
q(\mathbf{0}). $$
\vspace{-2mm}

\noindent Noting that $q(\mathbf{0}) = 0,$ the approximation error at $z = -\mathbf{1/2}$ is

\vspace{-2mm}
\begin{align*}
  \big|q(z) - \hat q(z)\big| \quad
  =& \quad \big|\|z\|_2^2 - \langle\mathbf{1},z\rangle\big| \\
  =& \quad \bigg| \frac{d}{4} + \frac{d}{2} \bigg| \quad = \quad \frac{3d}{4},
\end{align*}
\vspace{-2mm}

\noindent while plugging the constants into the error bound from the theorem gives

\vspace{-2mm}
\begin{align*}
  \big|q(z) - \hat q(z)\big| \quad
  \leq& \quad \frac{\gamma \|z - x_0\|_2^2}{2} + \sqrt{d} \frac{\gamma k^2}
      {2 \sigma_d} \|z - x_0\|_2 \\
  =& \quad \|z\|_2^2 + \sqrt{d} \|z\|_2 \\
  =& \quad \frac{d}{4} + \frac{d}{2} \quad = \quad \frac{3d}{4}.
\end{align*}
\vspace{-2mm}

\noindent In light of this error bound, an empirical evaluation of
presented interpolation and regression algorithms follows.

%% ===================================================================
\vspace{-2mm}
\section{Analytic Test of Convergence}
\label{sec:analytic}

The theoretical results constructed in Section \ref{sec:theory} for
(piecewise) linear interpolation are promising and apply directly to
Delaunay interpolation, however they are difficult to interpret in
context with approximation algorithms that do not have similar known
uniform error bounds. For that reason, an analytic function is used to
test the error of interpolants and regressors given an increasing
number of examples and increasing relative random error at data
points.

@@

This section extends the comparison of interpolation and regression
algorithms to a sample of real-world problems. Five different data
sets of varying dimension and application are utilized to construct
approximations and compare the accuracy of different techniques.

@@

\begin{table}
  \renewcommand{\arraystretch}{1.3}
  \centering
  \begin{tabular}{c|c|c|c|c}
               & $p = .05$         & $p = .01$         & $p = .001$        & $p = 10^{-6}$\\
    \hline
    Delaunay   & $\mathbf{50.3}\%$ & $\mathit{43.5}\%$ & $\mathit{36.2}\%$ & $\mathit{24.7}\%$\\
    ShepMod    & $\mathit{51.4}\%$ & $44.8\%$          & $38.1\%$          & $27.7\%$\\
    Voronoi    & $52.6\%$          & $\mathbf{43.4}\%$ & $\mathbf{34.4}\%$ & $\mathbf{19.1}\%$\\
    BoxSplines & $99.4\%$          & $98.5\%$          & $96.6\%$          & $89.3\%$\\
  \end{tabular}
  \caption{Numerical counterpart of the histogram data presented in
    Figure \ref{fig:throughput-prediction}. The columns display the
    percent of null hypothesis rejections by the KS-test when provided
    different selections of $p$-values for each algorithm. The
    algorithm with the lowest rejection rate at each $p$ is boldface,
    while the second lowest is italicized.}
  \label{table:null-hypothesis-results}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l}
    Algorithm & \multicolumn{2}{c|}{Avg. \% Best} & \multicolumn{2}{c|}{\multilinecell{Avg. Fit or \\ Prep. Time (s)}} & \multicolumn{2}{c}{Avg. App. Time (s)}\\
    \hline
    MARS        & \quad\quad$4$&$5$          & \quad\quad$20$&$0$s        & \qquad\quad $0$&$001$s\\
    SVR         & $\mathit{19}$&$\mathit{5}$ & $\mathbf{0}$&$\mathbf{5}$s & $\mathbf{0}$&$\mathbf{0001}$s\\
    MLP         & $\mathbf{43}$&$\mathbf{1}$ & $200$&$0$s                 & $0$&$001$s\\
    Delaunay    & $5$&$2$                    & $1$&$0$s                   & $1$&$0$s\\
    ShepMod     & $18$&$0$                   & $\textit{0}$&$\textit{7}$s & $\mathbf{0}$&$\mathbf{0001}$s\\
    LSHEP       & $8$&$4$                    & $2$&$0$s                   & $\mathbf{0}$&$\mathbf{0001}$s\\
    Voronoi     & $0$&$5$                    & $1$&$0$s                   & $0$&$04$s\\
    BoxSplines  & $3$&$5$                    & $0$&$8$s                   & $\mathit{0}$&$\mathit{0005}$s\\
  \end{tabular}
  \caption{This average of Appendix Tables
    \ref{table:best-forest-fire}, \ref{table:best-parkinsons},
    \ref{table:best-weather}, and \ref{table:best-credit-card}
    provides a gross summary of overall results. The columns display
    (weighted equally by data set, \textit{not} points) the average
    frequency with which any algorithm provided the lowest absolute
    error approximation, the average time to fit/prepare, and the
    average time required to approximate one point. The times have
    been rounded to one significant digit, as reasonably large
    fluctuations may be observed due to implementation hardware.
    Interpolants provide the lowest error approximation for nearly one
    third of all data, while regressors occupy the other two
    thirds. This result is obtained without any customized tuning or
    preprocessing to maximize the performance of any given
    algorithm. In practice, tuning and preprocessing may have large
    effects on approximation performance.}
  \label{table:avg-performance}
\end{table}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l|r@{.}l|r@{.}l}
    \hline
    Algorithm & \multicolumn{2}{c}{Min}       & \multicolumn{2}{c}{$25^{th}$} & \multicolumn{2}{c}{$50^{th}$} & \multicolumn{2}{c}{$75^{th}$} & \multicolumn{2}{c|}{Max}\\
    \hline
    MARS      & $0$&$00984$                   & $3$&$11$                      & $7$&$01$                      & $\mathit{11}$&$\mathit{7}$    & $1090$&$0$\\
    SVR       & $0$&$0118$                    & $\mathbf{0}$&$\mathbf{615}$   & $\mathbf{0}$&$\mathbf{931}$   & $\mathbf{5}$&$\mathbf{89}$    & $1090$&$0$\\
    MLP       & $0$&$0426$                    & $2$&$63$                      & $5$&$27$                      & $14$&$0$                      & $1090$&$0$\\
    Delaunay  & $\mathbf{0}$&$\mathbf{0}$     & $1$&$98$                      & $5$&$37$                      & $13$&$1$                      & $\mathit{1080}$&$\mathit{0}$\\
    ShepMod   & $\mathbf{0}$&$\mathbf{0}$     & $1$&$93$                      & $6$&$27$                      & $16$&$0$                      & $1090$&$0$\\
    LSHEP     & $0$&$04$                      & $2$&$17$                      & $8$&$87$                      & $19$&$1$                      & $\mathbf{1070}$&$\mathbf{0}$\\
    Voronoi   & $\mathit{0}$&$\mathit{00982}$ & $3$&$65$                      & $7$&$56$                      & $15$&$6$                      & $1090$&$0$\\
    BoxSpline & $\mathbf{0}$&$\mathbf{0}$     & $\mathit{1}$&$\mathit{27}$    & $\mathit{4}$&$\mathit{61}$    & $12$&$6$                      & $1090$&$0$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    Figure \ref{fig:error-forest-fire}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    third quartile, and maximum absolute errors respectively. The
    minimum of each column is boldface, while the second lowest value
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-forest-fire}
\end{table}

\begin{table}[H]
  \centering
  \begin{tabular}{|c|r@{.}l| c |r@{.}l|r@{.}l|r@{.}l|}
    \cline{1-3}\cline{5-10}
    Algorithm & \multicolumn{2}{c|}{\% Best}   &  & \multicolumn{2}{c|}{Fit/Prep. Time (s)} & \multicolumn{2}{c|}{App. Time (s)} & \multicolumn{2}{c|}{Total App. Time (s)}\\
    \cline{1-3}\cline{5-10}
    MARS      & \quad$7$&$3$                   &  & \quad\quad$29$&$1$                      & \quad$0$&$00137$                   & \quad\quad\quad$0$&$0686$\\
    SVR       & $\mathbf{78}$&$\mathbf{0}$     &  & $\mathbf{0}$&$\mathbf{00584}$           & $\mathit{0}$&$\mathit{0000620}$    & $\mathit{0}$&$\mathit{00310}$\\
    MLP       & $0$&$0$                        &  & $32$&$8$                                & $0$&$000871$                       & $0$&$0436$\\
    Delaunay  & $0$&$2$                        &  & $0$&$0151$                              & $0$&$0234$                         & $1$&$18$\\
    ShepMod   & $2$&$0$                        &  & $\mathit{0}$&$\mathit{00634}$           & $0$&$0000644$                      & $0$&$00322$\\
    LSHEP     & $5$&$1$                        &  & $0$&$0275$                              & $\mathbf{0}$&$\mathbf{0000463}$    & $\mathbf{0}$&$\mathbf{00231}$\\
    Voronoi   & $0$&$0$                        &  & $0$&$0152$                              & $0$&$000396$                       & $0$&$0198$\\
    BoxSpline & $\mathit{9}$&$\mathit{7}$      &  & $0$&$00724$                             & $0$&$0000978$                      & $0$&$00489$\\
    \cline{1-3}\cline{5-10}
  \end{tabular}
  \caption{The left above shows how often each algorithm had the
    lowest absolute error approximating forest fire data in Table
    \ref{table:error-forest-fire}. On the right columns are median fit
    time of 454 points, median time for one approximation, and median
    time approximating 50 points.}
  \label{table:best-forest-fire}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l|r@{.}l|r@{.}l}
    \hline
    Algorithm & \multicolumn{2}{c}{Min}                   & \multicolumn{2}{c}{$25^{th}$} & \multicolumn{2}{c}{$50^{th}$} & \multicolumn{2}{c}{$75^{th}$} & \multicolumn{2}{c|}{Max}\\
    \hline
    MARS      & $0$&$00948$                               & $9$&$98$                      & $20$&$4$                      & $32$&$9$                      & $863$&$0$\\
    SVR       & $0$&$00233$                               & $3$&$15$                      & $7$&$21$                      & $11$&$3$                      & $\mathbf{28}$&$\mathbf{6}$\\
    MLP       & $0$&$0000239$                             & $\mathit{0}$&$\mathit{533}$   & $\mathit{1}$&$\mathit{25}$    & $\mathbf{2}$&$\mathbf{84}$    & $39$&$3$\\
    Delaunay  & $\mathit{3}$&$\mathit{72 \times 10^{-12}}$ & $1$&$2$                       & $3$&$5$                       & $7$&$67$                      & $30$&$7$\\
    ShepMod   & $\mathbf{0}$&$\mathbf{0}$                 & $\mathbf{0}$&$\mathbf{255}$   & $\mathbf{0}$&$\mathbf{908}$   & $\mathit{3}$&$\mathit{43}$    & $34$&$5$\\
    LSHEP     & $0$&$00254$                               & $2$&$93$                      & $7$&$16$                      & $13$&$1$                      & $\mathit{29}$&$\mathit{0}$\\
    Voronoi   & $\mathbf{0}$&$\mathbf{0}$                 & $1$&$29$                      & $3$&$52$                      & $6$&$87$                      & $30$&$1$\\
    BoxSpline & $0$&$006$                                 & $4$&$3$                       & $8$&$91$                      & $15$&$1$                      & $45$&$3$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    Figure \ref{fig:error-parkinsons}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    third quartile, and maximum absolute errors respectively. The
    minimum of each column is boldface, while the second lowest value
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-parkinsons}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l|r@{.}l|r@{.}l}
    \hline
    Algorithm & \multicolumn{2}{c}{Min}                    & \multicolumn{2}{c}{$25^{th}$}              & \multicolumn{2}{c}{$50^{th}$}  & \multicolumn{2}{c}{$75^{th}$}  & \multicolumn{2}{c|}{Max}\\
    \hline
    MARS      & $\mathit{6}$&$\mathit{45 \times 10^{-15}}$ & $\mathbf{2}$&$\mathbf{70 \times 10^{-14}}$ & $1$&$66$                       & $1$&$96$                       & $\mathit{53}$&$\mathit{3}$\\
    SVR       & $0$&$0000915$                              & $0$&$0833$                                 & $0$&$263$                      & $\mathit{1}$&$\mathit{13}$     & $109$&$0$\\
    MLP       & $0$&$0000689$                              & $0$&$0337$                                 & $\mathbf{0}$&$\mathbf{0795}$   & $\mathbf{0}$&$\mathbf{264}$    & $\mathbf{5}$&$\mathbf{31}$\\
    Delaunay  & $\mathbf{0}$&$\mathbf{0}$                  & $0$&$187$                                  & $0$&$919$                      & $2$&$72$                       & $56$&$3$\\
    ShepMod   & $\mathbf{0}$&$\mathbf{0}$                  & $0$&$0957$                                 & $0$&$685$                      & $2$&$9$                        & $73$&$2$\\
    LSHEP     & $\mathbf{0}$&$\mathbf{0}$                  & $\mathit{0}$&$\mathit{0153}$               & $\mathit{0}$&$\mathit{106}$    & $1$&$17$                       & $113$&$0$\\
    Voronoi   & $\mathbf{0}$&$\mathbf{0}$                  & $0$&$43$                                   & $1$&$28$                       & $2$&$94$                       & $83$&$8$\\
    BoxSpline & $\mathbf{0}$&$\mathbf{0}$                  & $0$&$342$                                  & $1$&$59$                       & $5$&$53$                       & $119$&$0$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    Figure \ref{fig:error-weather}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    third quartile, and maximum absolute errors respectively. The
    minimum value of each column is boldface, while the second lowest
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-weather}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|c|r@{.}l| c |r@{.}l|r@{.}l|r@{.}l|}
    \cline{1-3}\cline{5-10}
    Algorithm & \multicolumn{2}{c|}{\% Best} &  & \multicolumn{2}{c|}{Fit/Prep. Time (s)}    & \multicolumn{2}{c|}{App. Time (s)} & \multicolumn{2}{c|}{Total App. Time (s)}\\
    \cline{1-3}\cline{5-10}
    MARS      & \,\,\,\,$10$&$7$             &  & \quad\quad\quad$\mathit{0}$&$\mathit{151}$ & \quad$0$&$000117$                  & \quad\quad\quad\,\,$0$&$0304$\\
    SVR       & $0$&$0$                      &  & $\mathbf{0}$&$\mathbf{133}$                & $\mathbf{0}$&$\mathbf{0000947}$    & $\mathbf{0}$&$\mathbf{0246}$\\
    MLP       & $\mathbf{60}$&$\mathbf{9}$   &  & $169$&$0$                                  & $0$&$00137$                        & $0$&$356$\\
    Delaunay  & $0$&$1$                      &  & $0$&$664$                                  & $0$&$886$                          & $230$&$0$\\
    ShepMod   & $3$&$5$                      &  & $0$&$265$                                  & $0$&$000128$                       & $0$&$0333$\\
    LSHEP     & $\mathit{28}$&$\mathit{4}$   &  & $0$&$874$                                  & $\mathit{0}$&$\mathit{0000975}$    & $\mathit{0}$&$\mathit{0254}$\\
    Voronoi   & $0$&$2$                      &  & $0$&$675$                                  & $0$&$0270$                         & $7$&$01$\\
    BoxSpline & $4$&$1$                      &  & $0$&$330$                                  & $0$&$000406$                       & $0$&$106$\\
    \cline{1-3}\cline{5-10}
  \end{tabular}
  \caption{Left table shows how often each algorithm had the lowest
    absolute error approximating Sydney rainfall data in Table
    \ref{table:error-weather}. On the right columns are median fit
    time of 2349 points, median time for one approximation, and median
    time approximating 260 points.}
  \label{table:best-weather}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l|r@{.}l|r@{.}l}
    \hline
    Algorithm & \multicolumn{2}{c}{Min}                    & \multicolumn{2}{c}{$25^{th}$} & \multicolumn{2}{c}{$50^{th}$} & \multicolumn{2}{c}{$75^{th}$} & \multicolumn{2}{c|}{Max}\\
    \hline
    MARS      & $5$&$36$                                   & $3610$&$0$                    & $4580$&$0$                    & $5450$&$0$                    & $13400$&$0$\\
    SVR       & $0$&$00706$                                & $8$&$14$                      & $\mathit{13}$&$\mathit{0}$    & $41$&$6$                      & $7690$&$0$\\
    MLP       & $0$&$00151$                                & $\mathbf{1}$&$\mathbf{6}$     & $\mathbf{3}$&$\mathbf{86}$    & $\mathbf{8}$&$\mathbf{34}$    & $\mathbf{604}$&$\mathbf{0}$\\
    Delaunay  & $\mathbf{0}$&$\mathbf{0}$                  & $\mathit{2}$&$\mathit{69}$    & $13$&$8$                      & $\mathit{35}$&$\mathit{0}$    & $\mathit{4840}$&$\mathit{0}$\\
    ShepMod   & $\mathbf{0}$&$\mathbf{0}$                  & $4$&$21$                      & $17$&$3$                      & $51$&$6$                      & $6510$&$0$\\
    LSHEP     & $1$&$27$                                   & $199$&$0$                     & $260$&$0$                     & $343$&$0$                     & $6530$&$0$\\
    Voronoi   & $\mathit{2}$&$\mathit{89 \times 10^{-10}}$ & $14$&$7$                      & $32$&$8$                      & $52$&$9$                      & $4860$&$0$\\
    BoxSpline & $\mathbf{0}$&$\mathbf{0}$                  & $12$&$4$                      & $35$&$0$                      & $90$&$1$                      & $7690$&$0$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    Figure \ref{fig:error-credit-card}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    third quartile, and maximum absolute errors respectively. The
    minimum value of each column is boldface, while the second lowest
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-credit-card}
\end{table}
